rdryad
======

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![R-check](https://github.com/ropensci/rdryad/workflows/R-check/badge.svg)](https://github.com/ropensci/rdryad/actions?query=workflow%3AR-check)
[![codecov](https://codecov.io/gh/ropensci/rdryad/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/rdryad)
[![cran checks](https://cranchecks.info/badges/worst/rdryad)](https://cranchecks.info/pkgs/rdryad)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/rdryad)](https://github.com/r-hub/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/rdryad)](https://cran.r-project.org/package=rdryad)

`rdryad` is a package to interface with the Dryad data repository.

General Dryad API documentation: https://datadryad.org/api/v2/docs/

rdryad docs: https://docs.ropensci.org/rdryad/

## Installation

Install Dryad from CRAN

```{r eval=FALSE}
install.packages("rdryad")
```

development version:

```{r eval=FALSE}
remotes::install_github("ropensci/rdryad")
```

```{r}
library('rdryad')
```

## Meta

* Please [report any issues or bugs](https://github.com/ropensci/rdryad/issues).
* License: MIT
* Get citation information for `rdryad` in R doing `citation(package = 'rdryad')`
* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

### Data provided by...

Data is provided from the Dryad API.
